Multi sky-view\\ 3D aerosol distribution recovery

### 2013-09-22 article.tex
Fixed style corrections

\author{Amit~Aides,\authnote{1*} Yoav~Y.~Schechner,\authnote{1}
  Vadim~Holodovsky\authnote{1}, Michael~J.~Garay\authnote{2} and Anthony~B.~Davis\authnote{2}}

@@

\bibitem{Stern2006}
A.~Stern and B.~Javidi, \enquote{{Three-dimensional image sensing,
  visualization, and processing using integral imaging},} Proceedings of the
  IEEE \textbf{94} (2006).

\bibitem{kim}
J.~Kim, D.~Lanman, Y.~Mukaigawa, and R.~Raskar, \enquote{{Descattering
  transmission via angular filtering},} in \enquote{Proc. ECCV' 10,}
  (Springer-Verlag, Berlin, Heidelberg, 2010), pp. 86--99.

@@

\bibitem{Mishchenko2007}
M.~I. Mishchenko and I.~V. Geogdzhayev, \enquote{{Satellite remote sensing
  reveals regional tropospheric aerosol trends.}} Optics express \textbf{15},
  7423--38 (2007).

@@

\bibitem{Namer2009}
E.~Namer, S.~Shwartz, and Y.~Y. Schechner, \enquote{{Skyless polarimetric
  calibration and visibility enhancement.}} Optics express \textbf{17}, 472--93
  (2009).

\bibitem{Bluestone2001}
A.~Bluestone, G.~Abdoulaev, C.~Schmitz, R.~Barbour, and A.~Hielscher,
  \enquote{{Three-dimensional optical tomography of hemodynamics in the human
  head},} Optics express \textbf{9}, 272--86 (2001).

@@

\bibitem{Cosofret2009}
B.~R. Cosofret, D.~Konno, A.~Faghfouri, H.~S. Kindle, C.~M. Gittins, M.~L.
  Finson, T.~E. Janov, M.~J. Levreault, R.~K. Miyashiro, and W.~J. Marinelli,
  \enquote{{Imaging sensor constellation for tomographic chemical cloud
  mapping},} Applied optics \textbf{48}, 1837--52 (2009).

@@

\bibitem{Cornette1995}
W.~M. Cornette and J.~G. Shanks, \enquote{{Physically reasonable analytic
  expression for the single-scattering phase function: errata.}} Applied optics
  \textbf{34}, 641 (1995).

@@

\bibitem{devroye1986sample}
L.~Devroye, \enquote{{Sample-based non-uniform random variate generation},} in
  \enquote{Proceedings of the 18th conference on Winter simulation,}  (ACM,
  1986), pp. 260--265.

\bibitem{Hong2004}
S.-H. Hong, J.-S. Jang, and B.~Javidi, \enquote{{Three-dimensional volumetric
  object reconstruction using computational integral imaging.}} Optics express
  \textbf{12}, 483--91 (2004).

@@

\bibitem{Pust2011}
N.~J. Pust, A.~R. Dahlberg, M.~J. Thomas, and J.~a. Shaw, \enquote{{Comparison
  of full-sky polarization and radiance observations to radiative transfer
  simulations which employ AERONET products.}} Optics express \textbf{19},
  18602--13 (2011).

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in Ref.~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we follow
Ref.~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}a uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}.

The {\em Haze Front} scene in \cref{fig:distributions}b uses an
ellipsoid degenerated to an elliptic cylinder that partly enters the
analyzed volume. It is 32km long (only part of which enters the
volume), 4km thick and centered at altitude 5km. The front stretches
across the domain width.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}a):
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\linewidth}\small{\input{images/mcgrid.pdf_tex}}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}[left], rendered using MC.
    [c] Cross section along the $X$-Axis of the MC simulation,
    single-scattering simulation and a single-scattering image created
    from the reconstructed distribution
    (\cref{sec:optimization-results}).}
  \label{fig:mcgrid}
\end{figure}

@@

The quality of MC increases with the number of photons launched.
\cref{fig:mcgrid}b shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].  A
comparison of a sample horizontal cross section is shown in
\cref{fig:mcgrid}c.

@@

\cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}. In
\cref{fig:results}a,b, the single-scattering model was used both
in rendering of the raw images, and in the estimation algorithm. In
\cref{fig:results}c,d, the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in \cref{fig:results}a,b stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}. The total estimation
error can be quantified by the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 
the total mass relative difference is
$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
The overall mass is recovered, but for 6.5\% loss. For local errors,
 $\epsilon=\|
\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
  In
\cref{fig:results}a,b, respectively $\epsilon=0.14$ and
$\epsilon=0.20$.  In \cref{fig:results}c,d, both cases have
$\epsilon=0.65$.

>>>>

\author{Amit~Aides,\authnote{1*} Yoav~Y.~Schechner,\authnote{1}
  Vadim~Holodovsky,\authnote{1} Michael~J.~Garay\authnote{2} and Anthony~B.~Davis\authnote{2}}

@@

\bibitem{Stern2006}
A.~Stern and B.~Javidi, \enquote{{Three-dimensional image sensing,
  visualization, and processing using integral imaging},} Proceedings of the
  IEEE \textbf{94.3} (2006).

\bibitem{kim}
J.~Kim, D.~Lanman, Y.~Mukaigawa, and R.~Raskar, \enquote{{Descattering
  transmission via angular filtering},} in \emph{Proc. ECCV' 10,}
  (Springer-Verlag, Berlin, Heidelberg, 2010), pp. 86--99.

@@

\bibitem{Mishchenko2007}
M.~I. Mishchenko and I.~V. Geogdzhayev, \enquote{{Satellite remote sensing
  reveals regional tropospheric aerosol trends},} \opex \textbf{15},
  7423--38 (2007).

@@

\bibitem{Namer2009}
E.~Namer, S.~Shwartz, and Y.~Y. Schechner, \enquote{{Skyless polarimetric
  calibration and visibility enhancement},} \opex \textbf{17}, 472--93
  (2009).

\bibitem{Bluestone2001}
A.~Bluestone, G.~Abdoulaev, C.~Schmitz, R.~Barbour, and A.~Hielscher,
  \enquote{{Three-dimensional optical tomography of hemodynamics in the human
  head},} \opex \textbf{9}, 272--86 (2001).

@@

\bibitem{Cosofret2009}
B.~R. Cosofret, D.~Konno, A.~Faghfouri, H.~S. Kindle, C.~M. Gittins, M.~L.
  Finson, T.~E. Janov, M.~J. Levreault, R.~K. Miyashiro, and W.~J. Marinelli,
  \enquote{{Imaging sensor constellation for tomographic chemical cloud
  mapping},} \ao \textbf{48}, 1837--52 (2009).

@@

\bibitem{Cornette1995}
W.~M. Cornette and J.~G. Shanks, \enquote{{Physically reasonable analytic
  expression for the single-scattering phase function: errata},} \ao
  \textbf{34}, 641 (1995).

@@

\bibitem{devroye1986sample}
L.~Devroye, \enquote{{Sample-based non-uniform random variate generation},} in
  \emph{Proceedings of the 18th conference on Winter simulation,}  (ACM,
  1986), pp. 260--265.

\bibitem{Hong2004}
S.-H. Hong, J.-S. Jang, and B.~Javidi, \enquote{{Three-dimensional volumetric
  object reconstruction using computational integral imaging},} \opex
  \textbf{12}, 483--491 (2004).

@@

\bibitem{Pust2011}
N.~J. Pust, A.~R. Dahlberg, M.~J. Thomas, and J.~a. Shaw, \enquote{{Comparison
  of full-sky polarization and radiance observations to radiative transfer
  simulations which employ AERONET products},} \opex \textbf{19},
  18602--18613 (2011).

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}.

The {\em Haze Front} scene in \cref{fig:distributions}(b) uses an
ellipsoid degenerated to an elliptic cylinder that partly enters the
analyzed volume. It is 32km long (only part of which enters the
volume), 4km thick and centered at altitude 5km. The front stretches
across the domain width.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}(a)):
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\linewidth}\small{\input{images/mcgrid.pdf_tex}}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}[left], rendered using MC.
    [c] Cross section along the $X$-Axis of the MC simulation,
    single-scattering simulation and a single-scattering image created
    from the reconstructed distribution
    (\cref{sec:optimization-results}).}
  \label{fig:mcgrid}
\end{figure}

@@

The quality of MC increases with the number of photons launched.
\cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].  A
comparison of a sample horizontal cross section is shown in
\cref{fig:mcgrid}(c).

@@

\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}. In
Figs.~\ref{fig:results}(a) and (b), the single-scattering model was used both
in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}. The total estimation
error can be quantified by the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 
the total mass relative difference is
$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
The overall mass is recovered, but for 6.5\% loss. For local errors,
 $\epsilon=\|
\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
$\epsilon=0.65$.
